An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-03-23 EconGrowth-R-Functions.Rnw
Beginning the process of making graphs of CI vs. parameters. Have now implemented graphs for SF model.

############################
# Aggregates the single-factor results into a big data table for the given factor.
##
singleFactorParamsTable <- function(factor){
  #Do rbind on the results of creating a row in the table for every country abbreviation that we know.
  dataSF <- do.call("rbind", lapply(countryAbbrevs, singleFactorCountryRow, factor=factor))
  if (factor == "K"){
    factorString <- "$\\alpha$"
  } else if (factor == "L"){
    factorString <- "$\\beta$"
  } else {
    factorString <- "$\\gamma$"
  }
  colnames(dataSF) <- c(" ", "$\\lambda$", " ", 
                        " ", factorString,  " ")
  rownames(dataSF) <- countryAbbrevs
  tableSF <- xtable(dataSF, 
                    caption=paste("Single-factor model (with $", tolower(factor), "$) parameters for 1980-2011 (US, UK, JP), 1991-2010 (CN and ZA), and 1991-2011 (SA, IR, TZ, and ZM). (Parameter estimates beneath symbol. 95\\% confidence interval bounds to left and right.)", sep=""), 
                    label=paste("tab:SF_Parameters_With_", factor, sep=""),
                    digits = c(1, 4,4,4, 2,2,2),
                    align = "r|ccc|ccc") #Sets alignment of the numbers in the columns
  return(tableSF)
}

>>>>

########################
# Aggregates the single-factor results intoa a big data frame for the given factor
##
singleFactorParamsDF <- function(factor){
  #Do rbind on the results of creating a row in the table for every country abbreviation that we know.
  dataSF <- do.call("rbind", lapply(countryAbbrevs, singleFactorCountryRow, factor=factor))
  #Add names to the rows and columns
  colnames(dataSF) <- list("lowerCI_lambda", "lambda", "upperCI_lambda", "lowerCI_m", "m", "upperCI_m")
  rownames(dataSF) <- countryAbbrevs
  return(dataSF)
}

############################
# Aggregates the single-factor results into a big data table for the given factor.
##
singleFactorParamsTable <- function(factor){
  dataSF <- singleFactorParamsDF(factor)
  if (factor == "K"){
    factorString <- "$\\alpha$"
  } else if (factor == "L"){
    factorString <- "$\\beta$"
  } else {
    factorString <- "$\\gamma$"
  }
  colnames(dataSF) <- c(" ", "$\\lambda$", " ", 
                        " ", factorString,  " ")
  rownames(dataSF) <- countryAbbrevs
  tableSF <- xtable(dataSF, 
                    caption=paste("Single-factor model (with $", tolower(factor), "$) parameters for 1980-2011 (US, UK, JP), 1991-2010 (CN and ZA), and 1991-2011 (SA, IR, TZ, and ZM). (Parameter estimates beneath symbol. 95\\% confidence interval bounds to left and right.)", sep=""), 
                    label=paste("tab:SF_Parameters_With_", factor, sep=""),
                    digits = c(1, 4,4,4, 2,2,2),
                    align = "r|ccc|ccc") #Sets alignment of the numbers in the columns
  return(tableSF)
}

### 2013-03-23 EconGrowth.Rnw
Beginning the process of making graphs of CI vs. parameters. Have now implemented graphs for SF model.

@@

\noindent to historical data where the factor of production ($f$) is any of $k$, $l$, $q$, $x$, or $u$, and the exponent ($m$) is $\alpha$ for $k$, $\beta$ for $l$, or $\gamma$ for $q$, $x$, and $u$.

@@

\noindent where $e$ can be any of thermal energy ($q$), exergy ($x$), or useful work ($u$).

@@

\noindent where $e$ is any of $q$, $x$, or $u$; $\sigma$, $\gamma_E$, $\beta$, $\lambda_L$, and $\lambda_E$ are fitting parameters; $\mathrm{e}$ is the base of the natural logarithm; and the sum $\alpha + \beta$ is constrained to unity.

@@

\noindent where $e$ is any of $q$, $x$, or $u$; $a_0$ and $c_t$ are fitting parameters; and $\mathrm{e}$ is the base of the natural logarithm.

>>>>

<<CIvsParam_Graph, eval=TRUE>>=
# plot(1:9, rep(1, 9), pch=LETTERS)
# xyplot(rep(1:9) ~ 1:9, pch=LETTERS)
# xyplot(rep(1:9) ~ 1:9, pch="US")
# states <- data.frame(state.x77, 
#                           state.name = dimnames(state.x77)[[1]], 
#                           state.region = state.region) 
#      xyplot(Murder ~ Population | state.region, data = states, 
#             groups = state.name, 
#             panel = function(x, y, subscripts, groups) { 
#                 ltext(x = x, y = y, labels = groups[subscripts], cex=1, 
#                       fontfamily = "HersheySans") 
#             }) 
# print(states)

#######################
# Creates a plot of confidence interval vs. value of a parameter with symbols being the 2-letter abbreviation
# for each country.
# 
# model the model function you want to use. One of SF, CD, CDe, CES, or LINEX.
# param the parameter you want to plot. The options depend upon the model you want:
#       SF: lambda or m
#       CD: lambda, alpha, or beta
#      CDe: lambda, alpha, beta, or gamma
#      CES: gamma, lambda, delta_1, sigma_1, delta, or sigma
#    LINEX: a_0 or c_t
# energyType the energy type you want. One of Q, X, or U
# factor the factor you want to use in a single-factor model, if needed. One of K, L, Q, X, or U.
##
CIvsParamPlot <- function(model, param, energyType=NA, factor=NA){
print("inside CIvsParamPlot")
  if (model == "SF"){
    data <- singleFactorParamsDF(factor)
    if (param == "lambda"){
      # Want lambda
      x <- subset(data, select=lambda) # The column of lambdas
      colnames(x) <- "lambda"
      xLabel <- "$\\lambda$"
      y <- subset(data, select=upperCI_lambda) - subset(data, select=lowerCI_lambda) # A column of CI values
      colnames(y) <- "CI"
      yLabel <- paste("95\\% CI on", xLabel)
      data <- cbind(x, y)
      data <- data.frame(data)
    } else if (param == "m"){
      # Want m
      x <- subset(data, select=m) # The column of lambdas
      colnames(x) <- "m"
      if (factor == "K"){xLabel <- "$\\alpha$"}
      else if (factor == "L"){xLabel <- "$\\beta$"}
      else if ((factor == "Q") || (factor == "X") || (factor == "U")){xLabel <- "$\\gamma$"}
      y <- subset(data, select=upperCI_m) - subset(data, select=lowerCI_m) # A column of CI values
      colnames(y) <- "CI"
      yLabel <- paste("95\\% CI on", xLabel)
      data <- cbind(x, y)
      data <- data.frame(data)
    }
  }
  if (model == "CD"){

  }
  if (model == "CDe"){

  }
  if (model == "CES"){

  }
  if (model == "LINEX"){

  }
#   plot <- xyplot(rep(1:9) ~ 1:9,
#                  panel = function(x, y){
# print(x)
# print(y)
#                    ltext(x = x, y = y, labels=countryAbbrevsAlph)
#                  })
print(data)
print(xLabel)
print(yLabel)
  # data[ , 1] is the column that contains the value of the parameter
  # data[ , 2] is the column that contains confidence intervals
  plot <- xyplot(data[ , 2] ~ data[ , 1],
                 xlab=list(label=xLabel),
                 ylab=list(label=yLabel),
                 panel = function(x, y){
                   ltext(x=x, y=y, labels=rownames(data))
                 })
  return(plot)
}
CIvsParamPlot(model="SF", param="m", factor="U")
@

@@

\noindent to historical data where the factor of production ($f$) is one of $k$, $l$, $q$, $x$, or $u$, and the exponent ($m$) is $\alpha$ for $k$, $\beta$ for $l$, or $\gamma$ for $q$, $x$, and $u$.

@@

\noindent where $e$ can be one of thermal energy ($q$), exergy ($x$), or useful work ($u$).

@@

\noindent where $e$ is one of $q$, $x$, or $u$; $\sigma$, $\gamma_E$, $\beta$, $\lambda_L$, and $\lambda_E$ are fitting parameters; $\mathrm{e}$ is the base of the natural logarithm; and the sum $\alpha + \beta$ is constrained to unity.

@@

\noindent where $e$ is one of $q$, $x$, or $u$; $a_0$ and $c_t$ are fitting parameters; and $\mathrm{e}$ is the base of the natural logarithm.
